### 2016-08-07 Engine.tex
添加: Dividng AMT

As mentioned before, our engine consists of the filter module and the
verification module. In this section, we introduce the filter module,
while in the next section the verification module will be illustrated.

@@

The filter we adopted in our engine is proposed by
\cite{Lee2013}. Given the pattern set, as in the WM algorithm, only
the length-$lsp$ prefix of each pattern are considering in
constructing the filter, where $lsp$ is the \emph{length of the
  shortest pattern} in the pattern set. Similar to WM, the filtering
is based on character blocks (a character block is a short string
consisting of only a few characters) rather than single
characters. Given a block size $k$, the filter includes $lsp-k+1$
membership query bitmaps denoted as $B_1$, $B_2$, \dots, and
$B_{lsp-k+1}$, where each bitmap is a vector of $N$ bits. Let
$B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be the
$i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1 iff
there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
where $hash$ is a hash function that maps a $k$-symbol block to an
integer in the range of $[0, N-1]$.

@@

>>>>

As mentioned before, our engine consists of a filter module and a
verification module. In this section, we introduce the former, while
in the next section the latter will be illustrated.

@@

The filter we adopted in our engine is proposed by \cite{Lee2013},
which is an improvement of the filter in the WM algorithm. Given the
pattern set, as in the WM algorithm, only the length-$lsp$ prefix of
each pattern are considering in constructing the filter, where $lsp$
is the \emph{length of the shortest pattern} in the pattern
set. Similar to WM, the filtering is based on character blocks (a
character block is a merely short string consisting of only a few
characters) rather than single characters. Given a block size $k$, the
filter includes $lsp-k+1$ membership query bitmaps denoted as $B_1$,
$B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap is a vector of $N$
bits. Let $B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be
the $i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1
iff there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
where $hash$ is a hash function that maps a $k$-symbol block to an
integer in the range of $[0, N-1]$.

@@

\subsection{Further Improvements}
\label{sec:further improments}

The verification module presented above is pretty efficient, but there
are still some techniques that can further improve the time and space
efficiency of this module.

\subsubsection{Dividing the AMT}
\label{sec:divide amt}

The verification module we have just built is based on a big single
AMT which is constructed from the whole pattern set. Actually, we can
divide the big AMT into small ones and enable each verifying procedure
to refer to only one small AMT, by which the time for verifying can be
reduced. The division is based on the following observations.

As stated in the filter module, for a position $i$ of the text $T$, if
some pattern $p_j$ starts at $i$, there must be
$Hash[T[i+lss-k,k]] = Hash[p_j[lss-k+1,k]]$ (we call
$Hash[p_j[lss-k+1,k]]$ the \emph{signature} of $p_j$). This means that
we can group the patterns according to their signatures: patterns with
the same signature are grouped together to form a sub-pattern-set, and
for each sub-pattern-set we build a (small) AMT from it. In addition,
an index table is adopted to allow the corresponding AMT be retrieved
in $O(1)$ time by its signature. Now, the verification module is made
up of an index table and several small AMTs.

Particularly, once a suspicious position $i$ in $T$ is detected, the
value $Hash[T[i+lss-k,k]]$ is used as the index of the index table to
find the corresponding small AMT for verifying $i$. As the scale of
the AMT shr, the time for each verifying is reduced accordingly.
